Understanding the Impact of Socioeconomic and Regional Factors on Health and Educational Outcomes

### 2024-12-15 code.qmd
local to fix merge conflict

@@

(Rishika will add here)

>>>>

```{r}
library("dplyr") 
library(mice) 
library(sjlabelled) 
library(tidyverse) 
library("modelsummary") 
library(car)
library(GGally)
library(ggplot2)
library(patchwork)
library(caret)
library(pROC)
library(pander)
```

Imputation

```{r}
combined <- read.csv('https://github.com/wujenny214/F24_STATS_FINAL/raw/refs/heads/main/combined.csv')
```

```{r, echo= FALSE, warning = FALSE}
# Making the state_fac variable a factor variable for future use
combined <- combined |> mutate(State_fac = factor(combined$State), Region_fac = factor(combined$Region, levels=c('South', 'West', 'Northeast', 'Midwest')))
```

```{r, echo= FALSE, warning = FALSE}
## Imputation Code 
# In this block, we are looking to use predictive mean matching to combing regression methods and hot deck imputing to predicted value closest to the predicted value of the observation with missing data; we also needed to convert school funding adequacy imputed values to school funding categorical variable before using in models

# Perform the imputation
sub.imp <- mice(sub, m = 1, method = "pmm", print = FALSE, seed=3)
```

@@

```{r}
plot1 <- ggplot(final_df, aes(x = Residential.Segregation.Index, y = Life.Expectancy)) +
  geom_point(color='purple') +
  labs(x = "Residential Segregation", y = "Life Expectancy")+ 
  theme(plot.margin = margin(t = 20, r = 30, b = 20, l = 10),
axis.title.x = element_text(size = 8),
axis.title.y = element_text(size = 8))

plot2 <- ggplot(final_df, aes(x = Percent.Limited.Access.Healthy.Foods
, y = Life.Expectancy)) +
  geom_point(color = "green") +
  labs( x = "% Population With Limited Healthy Food Access") +
  theme(plot.margin = margin(t = 20, r = 20, b = 20, l = 20),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8))

plot3 <- ggplot(final_df, aes(x = Percent.Uninsured.Adults, y = Life.Expectancy)) +
  geom_point(color = "blue") +
  labs(x = "% Adult Population Without Health Insurance", y = "Life Expectancy")+ 
  theme(plot.margin = margin(t = 20, r = 20, b = 20, l = 20),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8))

plot1 + plot2 + plot3 + plot_layout(ncol = 2, nrow=2) + 
  plot_annotation(title = "Relationships Between Predictors and 
                  Life Expectancy Outcome",
                  theme = theme(
      plot.title = element_text(hjust=0.5)))
```
